\sysfull

### 2017-08-10 paper/coalescing.tex
coalescing figures added

\sys determines $C$ for a given operation based on the number of tasks completed during the last operational period. \sys begins execution in a coalesced task with an infinite $C$ value. With a continuous power supply, the system executes from the start with all tasks as coalesced tasks entirely avoiding the cost of committing state. On intermittent power, the system executes a sequence of tasks that is interrupted by a power failure. \sys explicitly tracks $S$, the number of tasks completed during the previous operating period. \sys assigns $C$ to be equal to half of the value of $S$. If more tasks in total are able to complete in an operating period, \sys attempts to coalesce more tasks during the next operating period. If fewer tasks complete, \sys attempts to coalesce fewer tasks during the next operating period. $S$ includes the count of both coalesced and committing tasks completed. If no committing task completes, i.e., execution does not make progress, \sys updates $S$ and attempts to coalesce fewer tasks during the next operating period.

\begin{figure}
	\centering
	%\subfloat[]{\includegraphics[width=\columnwidth]{figures/}\label{fig:}}\\
	%\subfloat[]{\includegraphics[width=\columnwidth]{figures/}\label{fig:}}
	\caption{\sys task coalescing process.}
	\label{ffig:coalescing_example}
\end{figure}

\noindent\textbf{Task Coalescing Illustration:} 
%
%Figure~\ref{fig:coalescing_example} illustrates how \sys coalesces tasks. Figure~\ref{fig:coalescing_example}(a) shows a sequence of six tasks executing in \sys with no coalescing, incurring the cost of commit at each task transition. Figure~\ref{fig:coalescing_example}(b) shows the same sequence of tasks executing as coalesced groups of three tasks. 
%
Figure~\ref{fig:coalescing_example} shows how \sys adapts the value of $C$ based on $S$. \sys executes 12 tasks in the first operating period, assigning $S$ to six. \sys completes only five of the six coalesced tasks in the next operating period and then power fails. \sys sets $S$ to two in the next operating period, coalescing pairs of tasks and successfully committing two pairs before power fails. Execution resumes at the start of the third pair of tasks with a coalescing factor of two. If a larger number of tasks successfully complete in the next operating period, i.e., $S$ is larger, $C$ correspondingly increases, allowing more aggressive coalescing.

>>>>

\sys determines $C$ for a given operation based on the number of tasks completed, $S$, during the last operational period. \sys begins execution in a coalesced task with an infinite $C$ value. With a continuous power supply, the system executes from the start with all tasks as coalesced tasks entirely avoiding the cost of committing state. On intermittent power, the system executes a sequence of tasks that is interrupted by a power failure. \sys explicitly tracks $S$ during the previous operating period. \sys assigns $C$ to be equal to half of the value of $S$. If more tasks in total are able to complete in an operating period, \sys attempts to coalesce more tasks during the next operating period. If fewer tasks complete, \sys attempts to coalesce fewer tasks during the next operating period. $S$ includes the count of both coalesced and committing tasks completed. If no committing task completes, i.e., execution does not make progress, \sys updates $S$ and attempts to coalesce fewer tasks during the next operating period.

\begin{figure}
	\centering
	\subfloat[Core of task coalescing: commit postponing]{\includegraphics[width=\columnwidth]{figures/coalescing_states}\label{fig:coalescing_example_states}}\\
	\subfloat[Adaptive task coalescing based on task failure history]{\includegraphics[width=\columnwidth]{figures/coalescing_flowchart}\label{fig:coalescing_example_flowchart}}
	\caption{\sys task coalescing process.}
	\label{fig:coalescing_example}
\end{figure}

\noindent\textbf{Task Coalescing Illustration:} Figure~\ref{fig:coalescing_example} illustrates how \sys coalesces tasks. Figure~\ref{fig:coalescing_example_states} (left) shows a sequence of three tasks executing in \sys with no coalescing, incurring the cost of commit at each task transition. The same figure shows the same sequence of tasks executing as coalesced groups of three tasks $C=2$ (center) and $C=3$ (right). Figure~\ref{fig:coalescing_example_flowchart} shows how \sys adapts the value of $C$ based on $S$. \sys executes eight tasks in the first operating period, assigning $C=4$. \sys completes only two of the four coalesced tasks in the next operating period and then power fails. \sys sets $C=(6+8+2)/2$ in the next operating period, coalescing pairs of tasks and successfully committing two pairs before power fails. Execution resumes at the start of the third pair of tasks with a coalescing factor of two. If a larger number of tasks successfully complete in the next operating period, i.e., $S$ is larger, $C$ correspondingly increases, allowing more aggressive coalescing.\todo{Rewrite this paragraph to reflect what is in the figure}{Przemek}
